%-------------------------
% Resume in Latex
% Author : Kasier Roy S. Narandan
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\begin{center}
    \textbf{\Huge \scshape Kasier Roy S. Narandan} \\ \vspace{1pt}
    \small xxxxxxxxxxxx $|$ \href{kasierroy@gmail.com}{\underline{kasierroy@gmail.com}} $|$
    \href{https://linkedin.com/in/kasierroy}{\underline{linkedin.com/in/kasierroy}} $|$
    \href{https://github.com/kasierroy}{\underline{github.com/kasierroy}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cebu Institute of Technology - University}{June 2014 -- April 2019}
      {Bachelor of Science in Computer Engineering (Cum Laude)}{Cebu, PH}
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, C\#, Python, Bash, Rust, Assembly} \\
     \textbf{VCS}{: Git, Svn, Github, Gitlab, Gerrit, Jenkins} \\
     \textbf{Debugger}{: Valgrind, gdb, Visual Studio CPU/Memory Profiler}\\
     \textbf{Coding Principle}{: SOLID, Design Patterns } \\
     \textbf{Frameworks}{: WPF, Yocto, MSTest} \\
     \textbf{IDE}{: Visual Studio, vim, atom} \\
     \textbf{Libraries}{: UIAutomation, boost, nuget} \\
     \textbf{OS}{: Linux, Windows}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Research and Development Engineer}{Sept. 2022 -- Present}
      {Advanced World Solutions, Inc.}{Cebu, PH}
      \resumeItemListStart
        \resumeItem{Refactored an entire project code framework to use proper Software Design Patterns.}
        \resumeItem{Developed Windows Service applications using C\#.}
        \resumeItem{Developed WPF applications in C\# .NET Framework.}
        \resumeItem{Developed Windows DLL library using C++.}
        \resumeItem{Collaborated with hardware team to ensure successful software development.}
        \resumeItem{Introduced CI/CD in existing projects.}
        \resumeItem{Introduced TDD in existing projects.}
        \resumeItem{Fixed hot-issue bugs reported by client.}
        \resumeItem{Participated in code reviews and provided feedback to peers.}
        \resumeItem{Reduced memory usage of existing applications by 20\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Firmware Engineer}{April 2019 -- Sept. 2022}
      {Lexmark Research and Development Corporation}{Cebu, PH}
      \resumeItemListStart
        \resumeItem{Designed and implemented printer features using C/C++.}
        \resumeItem{Designed and implemented special printer product client requests.}
        \resumeItem{Automated integration and unit tests of firmware submodules using C++ and Python.}
        \resumeItem{Automated firmware delivery processes using Bash and Python.}
        \resumeItem{Collaborated with cross-functional teams to ensure successful printer feature development.}
        \resumeItem{Used SNMP and NPAP printer protocols.}
        \resumeItem{Fixed crash issues using gdb debugging tool.}
        \resumeItem{Fixed memory leak issues using valgrind tool.}
        \resumeItem{Fixed valgrind and coverity issues.}
        \resumeItem{Fixed Code RED and field issues.}
        \resumeItem{Participated in code reviews and design discussions.}
        \resumeItem{Provided daily triage and recommendation of bug issues.}
        \resumeItem{Reduced automated tests duration by at least 40\%.}
    \resumeItemListEnd

    \resumeSubheading
      {Part-time College Instructor}{Nov 2019 -- April 2020}
      {Cebu Institute of Technology - University}{Cebu, PH}
      \resumeItemListStart
        \resumeItem{Taught embedded programming in microcontrollers using C.}
        \resumeItem{Taught embedded programming in microcontrollers in Assembly.}
        \resumeItem{Taught computer interfacing from microcontrollers using UART, Serial, & other protocols.}
        \resumeItem{Taught basic C programming language.}
        \resumeItem{Taught basic logic circuits.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

% TBA
%-----------PROJECT-----------
%\section{Project}
%  \resumeSubHeadingListStart
%    \resumeProjectHeading
%      {\textbf{PROJECT #1} $|$ \emph{Python, Git, Firebase}}{June 2018 -- April 2019}
%      \resumeItemListStart
%            \resumeItem{}
%      \resumeItemListEnd
%  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
